Contextual Combinatorial Cascading Bandits

### 2016-02-04 contextual combinatorial cascading bandits.tex
modify

First, we incorporate contextual information into cascading bandits.
In online recommendation, contextual information includes various user and item information, 
	and user behaviors in different contexts are different.
Therefore utilizing contextual information is crucial for personalized recommendation.
In network routing, temporal and spacial contextual information may also be useful to
	determine better routing paths.
Therefore, we incorporate contextual information into the cascading bandit formulation.
Second, cascading bandits studied in \cite{kveton2015cascading,kveton2015combinatorial}
	treats all positions in the cascading list equally, but in applications different positions
	may bring different rewards.
For example, in online recommendation, we usually prefer users to find their interested item
	in the list as early as possible to increase user satisfaction.
In network routing, we may prefer to hit a blocked edge as late as possible.
To model these preference, we introduce position discounts to the cascading bandit, and
	we show through experiments that incorporating position discounts may significantly
	improve the learning result.
Finally, we generalize the reward functions of \cite{kveton2015cascading,kveton2015combinatorial}
	that are based on disjunctive and conjunctive binary random variables to more general
	non-linear reward functions satisfying monotonicity and Lipschitz continuity conditions.
This generalization allows us to covers new realistic scenarios not covered in
	\cite{kveton2015cascading,kveton2015combinatorial}, and we give such an example
	in Section~\ref{sec:diss}.

@@

We first discuss several studies most relevant to our work.
Table \ref{table:outline} summarizes the different settings of these work, 
	which we will explain in details next.
A comparison of regret bounds by different methods is deferred to Section \ref{sec:diss},
	after we provide the full results of our regret bounds.

The work of \cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework with disjunctive objective, where the set of feasible actions form a uniform matroid, and the reward of an action is $1$ if there is at least one ``good'' item in the list. 
The combinatorial cascading bandits of \cite{kveton2015combinatorial} (refered to as 'CombCascade' in Table \ref{table:outline}) generalized the framework, where each feasible action is a subset of ground items under combinatorial constraints; it studied a problem of combinatorial bandits with conjunctive objective, where each feasible action is a chain of items, and reward is $1$ if all items are "good". 
Our work generalizes these model and involves both contextual information and position discounts.

@@

Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward. The paper \cite{li2010contextual} studied multi-armed bandit with context information, which recommends one item a time. A recent work \cite{qin2014contextual} (refered to as 'C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward. Their feedback is more informative than ours. We relax the feedback from semi-bandit to cascading, yet our algorithm achieves the same order of regret bound.

@@

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $w_{t, a} = \theta_*^{\top} x_{t,a}$ is proved in the following lemma.
\begin{lemma} %estimate of U
  \label{lem:estimateU}
  When Eq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
  $$
    0 \leq \bU_t(a) - w_{t,a} \leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
  $$
\end{lemma}
\begin{proof}
	Note $w_{t,a} = \theta_*^{\top} x_{t,a}$. By H\"{o}lder's inequality,
	\begin{align*}
		&\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} = \abs{[\bV_{t-1}^{1/2}(\hat{\theta}_{t-1} - \theta_{\ast})]^{\top} (\bV_{t-1}^{-1/2}x_{t,a})}\\
		\leq &~\norm{\bV_{t-1}^{1/2}(\hat{\theta}_{t-1} - \theta_{\ast})}_2 \norm{\bV_{t-1}^{-1/2}x_{t,a}}_2\\
		=&~\norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
		\leq&~ \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
	\end{align*}
	Because $1 - \theta_*^{\top} x_{t,a} \geq 0$ and
	\begin{align*}
		0 &\leq (\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}) - \theta_{\ast}^{\top}x_{t,a} \\
		&\leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}},
	\end{align*}
	the claimed result is obtained.
\end{proof}

@@

The Bernoulli random variables $\bw_{t}(a) \in \{0,1\}$ indicate the weight of item $a$ at time $t$ satisfying Eq.~\eqref{eq:expectation}. The learning agent observes the first position $k$ in the given action $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$ with $w_t(\ba_k^t)=0$. We also consider partial rewards: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.

The more items reveals, the more reward the agent should receive. This can be used to model scenarios such as online surveys, where questions are adaptively given, and the more questions observed, the more helpful to the survey conductor. Based on this, we assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time $t$, the learning agent observes $\bO_{t}, \bw_t(\ba_k^t), k \leq \bO_{t}$ and receives reward $\br_{t}$:
\begin{align*}
	\br_{t} &= \begin{cases}
		1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 1.
	\end{cases}\\
	%&=\begin{cases}
	%	1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i < k, \text{and } \bw_t(\ba_{k}^t) = 0,\\
	%	1 &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i\leq \abs{\bA_t}.
	%\end{cases}
\end{align*}

@@

We evaluated our algorithm, $C^3$-UCB, in a synthetic setting and two real applications. The results are compared with {\it CombCascade}, the most related study to ours, and demonstrate the advantage to involve contextual information and position discounts. In experiments, we set the position discounts $\gamma_k$ to be $\gamma^{k-1}$ for some $\gamma$.

@@

In the first experiment, we compared $C^3$-UCB to CombCascade on synthetic problems. This problem is a contextual cascading bandit with $L=100$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user. At first, we randomly chose a $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$. Then at each time $t$, we randomly assigned $x'_{t,a} \in \RR^{d-1}$ with $\|x'_{t,a}\|_2 = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$. This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} = \frac{1}{2}(\theta^{\top}x'_{t,a} + 1) \in [0,1]$. Next we generated the weight for arm $a$ at time $t$ by a random sample from the Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.

We conducted experiments in four settings. Under each setting, the learning agent chooses a set of $K$ items out of $L$ ground items. The first two are of disjunctive objective where the learning agent observes a prefix of the chosen $K$ items until the first one with weight $1$; the last two are of conjunctive objective where the learning agent observes from the first item until the first one with weight $0$. Notice that with $\gamma \leq 1$, the oracle selects a set of $K$ items with highest UCBs in their decreasing order. The results are shown in Fig.~\ref{fig:synthetic} and our algorithm outperforms {\it CombCascade} algorithm because they do not make use of the context information.

@@

In this experiment, we evaluated $C^3$-UCB on movie recommendation with data set {\it MovieLens} \cite{lam2013movie} of 2015.

The Learning problem is formulated as follows. There is a big sparse matrix $A \in \{0,1\}^{N_1 \times N_2}$ where $A(i,j) = 1$ denotes user $i$ has watched movie $j$. Next, we split $A$ as $H + F$ by putting $1$-entry in $A$ to $H$ or $F$ according to a Bernoulli distribution $\sim \mathrm{Ber}(p)$ for some fixed $p$. We regard $H$ as known information about history "what users have watched" and regard $F$ as future criterion. We use $H$ to derive feature vectors of both users and movies by SVD decomposition, $H = USM^{\top}$ where $U = (u_1; ...;u_{N_1})$ and $M = (m_1;...;m_{N_2})$. At every time $t$, we randomly choose a user $I_t \in [N_1]$. Then in the same spirit of \cite{li2010contextual}, use $x_{t,j} = u_{I_t}m_j^{\top}$, the outer product of $u_{I_t}$ and $m_{j}$, as the context information for each movie $j$. The real weight of movie $j$ at time $t$, $\bw_t(j)$, is $F(I_t,m)$.

For this experiment, we randomly chose $L=200$ movies and recommended $K=4$ movies at each time. We experimented with both $\gamma=1$ (no position discount) and $\gamma=0.9$, and compared our algorithm with {\it CombCascade}. The results for rewards are shown in Fig.\ref{fig:movielens} and demonstrate the advantage to involve context information in real applications.

@@

In the last experiment, we evaluated $C^3$-UCB on network routing problem with {\it RocketFuel} dataset \cite{spring2004measuring}.

The ground set $E$ is the set of links in the network. Before learning, the environment randomly chooses a $d$-dimensional vector $\theta_* \in [0,1]^d$. At each time $t$, a pair of source and destination nodes are randomly chosen and the feasible action set $\cS_t$ at time $t$ is all simple paths between the source and destination nodes. Any edge $a$ in the set $\cS$ is assigned with a random $d$-dimensional context vector $x_{t,a}$. Notice here both $\theta$ and $x$ have been processed like Section \ref{sec:ExpSyn} so that $\theta_*^{\top}x \in [0,1]$. The weight for each edge $a$ is a sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$. Then the learning agent recommends a feasible path $A = (a_1,...,a_{|A|})$ between source and destination nodes to maximize the expected reward in the conjunctive objective. We experimented with different position discounts and different networks. The results are shown in Fig.~\ref{fig:network} (a) (b).

We also experimented on the network with latency, where the latency on an edge is an exponential random variable with mean $\theta_{\ast}^{\top}x$ and the reward is $1$ if the latency is less than a tolerance $\tau = 0.75$. The comparison of rewards of our algorithm with {\it CombCascade} is shown in Fig.~\ref{fig:network} (c).

We also experimented on the influence of different $\gamma$'s to the regret. In recommendations, the position discounts represent users' satisfaction and the learning agent may not know its true value. Suppose the true position discount $\gamma^{\ast} = 0.9$ and the learning agent sets $\gamma$ by her experience. We experiment on different setting $\gamma \in \{0.8, 0.82, \ldots, 0.98, 1.0\}$ with the true criterion $\gamma^{\ast} = 0.9$. The regrets with different $\gamma$'s are illustrated in Figure~\ref{fig:network}(d), from which it can be seen that the regret is minimized around the true $\gamma^{\ast}$. The big gap between the regret at $\gamma = 1$ and $\gamma^{\ast} = 0.9$ shows that it significantly benefits by exploiting position discounts in the model when such discounts indeed exist in applications.

@@

In this paper, we propose contextual combinatorial cascading bandits with position discounts, where each action is an ordered list and only a prefix of the action is observed each time. We propose a C$^3$-UCB algorithm and prove a cumulative regret bound for general reward functions and two special reward functions. The experiments conducted demonstrate the advantage to involve context information and position discounts. A matching lower bound on the regret bound is left for a future study.

@@

\begin{lemma} %lem:DeltaEsimateWithP*
	\label{lem:DeltaEsimateWithP*}
	Suppose the Eq.~\eqref{eq:estimateTheta} holds for time $t-1$. Then
	$$
	\EE[R^{\alpha}(t, \bA_t) | \cH_t] \leq \frac{2B}{p^*} \EE \left[ \left.\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
	$$
\end{lemma}
\begin{proof}
	\begin{align}
		&\EE[R^{\alpha}(t, \bA_t)|\cH_t]  \nonumber \\
		=& \EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \label{eq:addOt}\\
		=& \EE \left[ \left. R^{\alpha}(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:removeE}\\
		\leq &\frac{1}{p^{\ast}} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:relaxpstar}\\
		\leq &\frac{2B}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:useradiusbound}\\
		\leq &\frac{2B}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right]. \label{eq:relaxindicator}
	\end{align}
	Equality \eqref{eq:addOt} is because when $\bA_t$ is fixed, $p_{t, \bA_t}$ is the probability of $\bO_t = \abs{\bA_t}$, and thus the inner expectation is $1$. Equality \eqref{eq:removeE} is because when the history $\cH_t$ is fixed, $\bA_t$ is fixed by the deterministic algorithm C$^3$-UCB, and thus there is no need to write the conditional expectation. Inequality~\eqref{eq:relaxpstar} is because $p_{t,\bA_t} \geq p^*$ by definition. Inequality~\eqref{eq:useradiusbound} is by Lemma \ref{lem:DeltaEstimate} and the fact $f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t)$, which is true because algorithm C$^3$-UCB selects action $\bA_t$ as the best action with respect to $\bU_t$. Inequality~\eqref{eq:relaxindicator} is by simply arguing on the two cases for the indicator function $\bOne\{\bO_t = \abs{\bA_t}\}$.
\end{proof}

@@

\begin{lemma} % lem:SumXiEstimateInDet
  \label{lem:SumXiEstimateInDet}
  \CLemmaSumXiEstimateInDet
\end{lemma}
\begin{proof}
	\begin{align}
	&\det(\bV_t) = \det\left(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k x_{t,\ba_k^{t}})(\gamma_k x_{t, \ba_k^{t}}^{\top}) \right) \nonumber \\
	&=\det(\bV_{t-1}) \notag \\
	&~~~\cdot \det \left(I + \sum_{k=1}^{\bO_t} \gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top} \right) \label{eq:Vfactor}\\
	&\geq \det(\bV_{t-1}) \left(1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right) \label{eq:detGeq} \\
	&\geq \det(\lambda I)\prod_{s=1}^{t} \left(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \right), \label{eq:repeatV}
	\end{align}
	where Equality~\eqref{eq:Vfactor} is by the fact that $V+U = V^{1/2} (I + V^{-1/2} U V^{-1/2}) V^{1/2}$ for a symmetric positive definite matrix $V$, Inequality \eqref{eq:detGeq} is due to Lemma \ref{lem:detTech}, and Inequality~\eqref{eq:repeatV} is by repeatedly applying Inequality \eqref{eq:detGeq}.

>>>>

First, we incorporate contextual information into cascading bandits.
In online recommendation, contextual information includes various user and item information, 
	and user behaviors in different contexts are different.
Therefore utilizing contextual information is crucial for personalized recommendation.
In network routing, temporal and spacial contextual information may also be useful to
	determine better routing paths.
Therefore, we incorporate contextual information into the cascading bandit formulation.
Second, cascading bandits studied in \cite{kveton2015cascading,kveton2015combinatorial}
	treats all positions in the cascading list equally, but in applications different positions
	may bring different rewards.
For example, in online recommendation, we usually prefer users to find their interested item
	in the list as early as possible to increase user satisfaction.
In network routing, we may prefer to hit a blocked edge as late as possible.
To model these preference, we introduce position discounts to the cascading bandit, and
	we show through experiments that incorporating position discounts may significantly
	improve the learning result.
Finally, we generalize the reward functions of \cite{kveton2015cascading,kveton2015combinatorial}
	that are based on disjunctive and conjunctive binary random variables to more general
	non-linear reward functions satisfying monotonicity and Lipschitz continuity conditions.
This generalization allows us to cover new realistic scenarios not covered in
	\cite{kveton2015cascading,kveton2015combinatorial}, and we give such an example
	in Section~\ref{sec:diss}.

@@

We first discuss several studies most relevant to our work.
Table \ref{table:outline} summarizes the different settings of these work, 
	which we will explain in details next.
A comparison of regret bounds by different methods is deferred to Section \ref{sec:diss},
	after we provide full results of our regret bounds.

The work of \cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework with disjunctive objective, where the set of feasible actions form a uniform matroid, and the reward of an action is $1$ if there is at least one ``good'' item in the list. 
The combinatorial cascading bandits of \cite{kveton2015combinatorial} (referred to as 'CombCascade' in Table \ref{table:outline}) generalized the framework, where each feasible action is a subset of ground items under combinatorial constraints; it studied a problem of combinatorial bandits with conjunctive objective, where each feasible action is a chain of items, and reward is $1$ if all items are "good". 
Our work generalizes these model and involves both contextual information and position discounts.

@@

Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward. The paper \cite{li2010contextual} studied multi-armed bandit with context information, which recommends one item a time. A recent work \cite{qin2014contextual} (referred to as 'C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward. Their feedback is more informative than ours. We relax the feedback from semi-bandit to cascading, yet our algorithm achieves the same order of regret bound.

@@

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $w_{t, a} = \theta_*^{\top} x_{t,a}$ is proved in the following lemma.
\begin{lemma} %estimate of U
  \label{lem:estimateU}
  When Ineq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
  $$
    0 \leq \bU_t(a) - w_{t,a} \leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
  $$
\end{lemma}
\begin{proof}
	Note $w_{t,a} = \theta_*^{\top} x_{t,a}$. By H\"{o}lder's inequality,
	\begin{align*}
		&\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} = \abs{[\bV_{t-1}^{1/2}(\hat{\theta}_{t-1} - \theta_{\ast})]^{\top} (\bV_{t-1}^{-1/2}x_{t,a})}\\
		\leq &~\norm{\bV_{t-1}^{1/2}(\hat{\theta}_{t-1} - \theta_{\ast})}_2 \norm{\bV_{t-1}^{-1/2}x_{t,a}}_2\\
		=&~\norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
		\leq&~ \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
	\end{align*}
	Because $1 - \theta_*^{\top} x_{t,a} \geq 0$ and
	\begin{align*}
		0 &\leq (\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}) - \theta_{\ast}^{\top}x_{t,a} \\
		&\leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}},
	\end{align*}
	the claimed result is obtained.
\end{proof}

@@

The Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ indicates the weight of item $a$ at time $t$ satisfying Eq. \eqref{eq:expectation}. The learning agent observes the first position $k$ in the given action $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$ with $w_t(\ba_k^t)=0$. We also consider partial rewards: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.

The more items reveals, the more reward the agent should receive. This can be used to model scenarios such as online surveys, where questions are adaptively given, and the more questions observed, the more helpful to the survey conductor. Based on this, we assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time $t$, the learning agent observes $\bO_{t}, \bw_t(\ba_k^t), k \leq \bO_{t}$ and receives reward $\br_{t}$:
\begin{align*}
	\br_{t} %&= \begin{cases}
		%1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 0,\\
		%1 &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 1.
	%\end{cases}\\
	&=\begin{cases}
		1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i < k, \text{and } \bw_t(\ba_{k}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i\leq \abs{\bA_t}.
	\end{cases}
\end{align*}

@@

We evaluate our algorithm, $C^3$-UCB, in a synthetic setting and two real applications. The results are compared with {\it CombCascade}, the most related study to ours, and demonstrate the advantage to involve contextual information and position discounts. In experiments, we set the position discounts $\gamma_k$ to be $\gamma^{k-1}$ for some $\gamma$.

@@

In the first experiment, we compare $C^3$-UCB to {\it CombCascade} on synthetic problems. This problem is a contextual cascading bandit with $L=100$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user. At first, we randomly choose a $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$. Then at each time $t$, we randomly assign $x'_{t,a} \in \RR^{d-1}$ with $\|x'_{t,a}\|_2 = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$. This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} = \frac{1}{2}(\theta^{\top}x'_{t,a} + 1) \in [0,1]$. Next we generate the weight for arm $a$ at time $t$ by a random sample from the Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.

We conduct experiments in four settings. Under each setting, the learning agent chooses a set of $K$ items out of $L$ ground items. The first two are of disjunctive objective where the learning agent observes a prefix of the chosen $K$ items until the first one with weight $1$; the last two are of conjunctive objective where the learning agent observes from the first item until the first one with weight $0$. Notice that with $\gamma \leq 1$, the oracle selects a set of $K$ items with highest UCBs in their decreasing order. The results are shown in Fig.~\ref{fig:synthetic} and our algorithm outperforms {\it CombCascade} algorithm because they do not make use of the context information.

@@

In this experiment, we evaluate $C^3$-UCB on movie recommendation with data set {\it MovieLens} \cite{lam2013movie} of 2015.

The Learning problem is formulated as follows. There is a big sparse matrix $A \in \{0,1\}^{N_1 \times N_2}$ where $A(i,j) = 1$ denotes user $i$ has watched movie $j$. Next, we split $A$ as $H + F$ by putting $1$-entry in $A$ to $H$ or $F$ according to a Bernoulli distribution $\sim \mathrm{Ber}(p)$ for some fixed $p$. We regard $H$ as known information about history "what users have watched" and regard $F$ as future criterion. We use $H$ to derive feature vectors of both users and movies by SVD decomposition, $H = USM^{\top}$ where $U = (u_1; ...;u_{N_1})$ and $M = (m_1;...;m_{N_2})$. At every time $t$, we randomly choose a user $I_t \in [N_1]$. Then in the same spirit of \cite{li2010contextual}, we use $x_{t,j} = u_{I_t}m_j^{\top}$, the outer product of $u_{I_t}$ and $m_{j}$, as the context information for each movie $j$. The real weight of movie $j$ at time $t$, $\bw_t(j)$, is $F(I_t,m)$.

For this experiment, we randomly choose $L=200$ movies and recommend $K=4$ movies at each time. We experiment with both $\gamma=1$ (no position discount) and $\gamma=0.9$, and compare our algorithm with {\it CombCascade}. The results for rewards are shown in Fig.\ref{fig:movielens} and demonstrate the advantage to involve contextual information in real applications.

@@

In the last experiment, we evaluate $C^3$-UCB on network routing problem with {\it RocketFuel} dataset \cite{spring2004measuring}.

The ground set $E$ is the set of links in the network. Before learning, the environment randomly chooses a $d$-dimensional vector $\theta_* \in [0,1]^d$. At each time $t$, a pair of source and destination nodes are randomly chosen and the feasible action set $\cS_t$ at time $t$ is all simple paths between the source and destination nodes. Any edge $a$ in the set $\cS_t$ is assigned with a random $d$-dimensional contextual information vector $x_{t,a}$. Notice here both $\theta$ and $x$ have been processed like in Section \ref{sec:ExpSyn} such that $\theta_*^{\top}x \in [0,1]$. The weight for each edge $a$ is a sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$. Then the learning agent recommends a feasible path $A = (a_1,...,a_{|A|})$ between source and destination nodes to maximize the expected reward in the conjunctive objective. We experiment on different position discounts. The results are shown in Fig.~\ref{fig:network} (a) (b).

Another experiment is conducted on the network with latency, where the latency on an edge is an exponential random variable with mean $\theta_{\ast}^{\top}x$ and the reward is $1$ if the latency is less than a tolerance $\tau = 0.75$. The comparison of the cumulative rewards of our algorithm with {\it CombCascade} is shown in Fig.~\ref{fig:network} (c).

We also conduct an experiment on the influence of different $\gamma$'s to the regret. In recommendations, the position discounts represent users' satisfaction and the learning agent may not know its true value. Suppose the true position discount $\gamma^{\ast} = 0.9$ and the learning agent sets $\gamma$ by her experience. We experiment on different $\gamma \in \{0.8, 0.82, \ldots, 0.98, 1.0\}$ with the true criterion $\gamma^{\ast} = 0.9$. The regrets with different $\gamma$'s are illustrated in Fig.~\ref{fig:network}(d), from which it can be seen that the regret is minimized around the true $\gamma^{\ast}$. The big gap between the regret at $\gamma = 1$ and $\gamma^{\ast} = 0.9$ shows that it significantly benefits by exploiting position discounts in the model when such discounts indeed exist in applications.

@@

In this paper, we propose contextual combinatorial cascading bandits with position discounts, where each action is an ordered list and only a prefix of the action is observed each time. We propose a C$^3$-UCB algorithm and prove a cumulative regret bound for general reward functions and two special reward functions. The experiments conducted demonstrate the advantage to involve contextual information and position discounts. A matching lower bound on the regret bound is left for a future study.

@@

\begin{lemma} %lem:DeltaEsimateWithP*
	\label{lem:DeltaEsimateWithP*}
	Suppose the Ineq.\eqref{eq:estimateTheta} holds for time $t-1$. Then
	$$
	\EE[R^{\alpha}(t, \bA_t) | \cH_t] \leq \frac{2B}{p^*} \EE \left[ \left.\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right| \cH_t \right].
	$$
\end{lemma}
\begin{proof}
	\begin{align}
		&\EE[R^{\alpha}(t, \bA_t)|\cH_t]  \nonumber \\
		=& \EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \label{eq:addOt}\\
		=& \EE \left[ \left. R^{\alpha}(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:removeE}\\
		\leq &\frac{1}{p^{\ast}} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:relaxpstar}\\
		\leq &\frac{2B}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:useradiusbound}\\
		\leq &\frac{2B}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right]. \label{eq:relaxindicator}
	\end{align}
	Eq.\eqref{eq:addOt} is because when $\bA_t$ is fixed, $p_{t, \bA_t}$ is the probability of $\bO_t = \abs{\bA_t}$, and thus the inner expectation is $1$. Eq.\eqref{eq:removeE} is because when the history $\cH_t$ is fixed, $\bA_t$ is fixed by the deterministic algorithm C$^3$-UCB, and thus there is no need to write the conditional expectation. Ineq.\eqref{eq:relaxpstar} is because $p_{t,\bA_t} \geq p^*$ by definition. Ineq.\eqref{eq:useradiusbound} is by Lemma \ref{lem:DeltaEstimate} and the fact $f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t)$, which is true because algorithm C$^3$-UCB selects action $\bA_t$ as the best action with respect to $\bU_t$. Ineq.\eqref{eq:relaxindicator} is by simply arguing on the two cases for the indicator function $\bOne\{\bO_t = \abs{\bA_t}\}$.
\end{proof}

@@

\begin{lemma} % lem:SumXiEstimateInDet
  \label{lem:SumXiEstimateInDet}
  \CLemmaSumXiEstimateInDet
\end{lemma}
\begin{proof}
	\begin{align}
	&\det(\bV_t) = \det\left(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k x_{t,\ba_k^{t}})(\gamma_k x_{t, \ba_k^{t}}^{\top}) \right) \nonumber \\
	&=\det(\bV_{t-1}) \notag \\
	&~~~\cdot \det \left(I + \sum_{k=1}^{\bO_t} \gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top} \right) \label{eq:Vfactor}\\
	&\geq \det(\bV_{t-1}) \left(1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right) \label{eq:detGeq} \\
	&\geq \det(\lambda I)\prod_{s=1}^{t} \left(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \right), \label{eq:repeatV}
	\end{align}
	where Eq.\eqref{eq:Vfactor} is by the fact that $V+U = V^{1/2} (I + V^{-1/2} U V^{-1/2}) V^{1/2}$ for a symmetric positive definite matrix $V$, Ineq.\eqref{eq:detGeq} is due to Lemma \ref{lem:detTech}, and Ineq.\eqref{eq:repeatV} is by repeatedly applying Ineq.\eqref{eq:detGeq}.

	Because
	$$
	\norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma_k x_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma_k^2 /\lambda,
	$$
	where $\lambda_{\min}(\bV_{s-1})$ is the minimum eigenvalue of $\bV_{s-1}$,  we have 
	$$
	\sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \frac{1}{\lambda} \sum_{k=1}^{K} \gamma_k^2 = C_\gamma /\lambda \leq 1
	$$
	Using the fact that $ 2\ln(1+u) \geq u$ for any $u \in [0,1]$, we get
	\begin{align*}
	&\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
	&\leq 2\sum_{s=1}^t\ln \left(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \right)\\
	& = 2 \ln \prod_{s=1}^{t} \left(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \right) \\
	&\le 2 \ln \left(\frac{\det(\bV_t)}{\det(\lambda I)} \right),
	\end{align*}
	where the last inequality is from Ineq.\eqref{eq:repeatV}.
\end{proof}
